### 2019-04-03 papers/journal/encoding.tex
Updated the 1.2

In the later synthesis problems, we will construct a similar QBF
formula with same first two parts and the last two are due the
requirements of the synthesis problem.
%
\subsubsection{Fixing VTS by adding molecules to the labels}
The system may also be fixed only by modifying labels on the edges or the nodes instead
of adding edges.
%
Here let us consider only adding molecules to the labels of edges.
%
In the following, the formula encodes that only $slimit$ edge labels may be added.
\begin{align*}
&\texttt{AddLabelEdge}(slimit) = 
\sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
& \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
& \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthLabel}(slimit) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
\end{align*} 
Similar to the previous encoding, we solve the
satisfiability of the above formula to obtain additional molecules
that may be added to the edge labels to satisfy the properties.

\subsubsection{Fixing VTS by learning activity functions}
Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

>>>>

In the later synthesis problems, we will construct a similar QBF
formula with same first two parts and the last two are due the
requirements of the synthesis problem.
%
\subsubsection{Fixing VTS by adding molecules to the labels}
The system may also be fixed only by modifying labels on the edges or the nodes instead
of adding edges.
%
Here let us consider only adding molecules to the labels of edges.
%
In the following, the formula encodes that only $slimit$ edge labels may be added.
%
\begin{align*}
&\texttt{AddLabelEdge}(slimit) = 
\sum~\texttt{UnknwonEdgeLabel}  \leq slimit\\
& \texttt{FixedForLabel} = \texttt{PresentCons} \land \texttt{UnknownActive} \land\\
& \quad \quad \lnot \Lor \texttt{AbsentE} \;\union\;
\texttt{AbsentNLabel} \;\union\;
\texttt{AbsentP}\\
&\texttt{SynthLabel}(slimit) = \\
& \quad\quad
(  \texttt{Consistancy}\land \texttt{Property} \land
\texttt{FixedForLabel} \land \texttt{AddLabelEdge}(slimit) )
\end{align*} 
%
Similar to the previous encoding, we solve the
satisfiability of the above formula to obtain additional molecules
that may be added to the edge labels to satisfy the properties.
%
\subsubsection{Fixing VTS by learning activity functions}
Now we consider a scenario where some of the activity functions for
some of the molecules are missing.
%
The activity functions are $\mu$-input Boolean functions.
%
First, we choose a class of formulas for the candidate functions.
%
We encode the candidates in a formula with parameters.
%
By assigning different values for the parameters, a solver may select
different candidates for the activity functions.
%
We will illustrate only one class of formulas.
%
However, we support other classes of formulas, for example, $k$-CNF.

### 2019-04-03 papers/journal/intro.tex
Updated the 1.2

\subsection{The model}
\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed.
\item Each compartment is in steady state, gain and loss of the molecules is balance.
\item Molecules are neither created nor destroyed.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
\item An active SNARE pair is necessary and sufficient for fusion. 
\end{enumerate}

%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%
\begin{example}
	%
	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool. The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.

\end{example}
\input{synth-dia}

>>>>

\subsection{The model}
\noindent The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed~\cite{braell1984glycoprotein}.
\item Each compartment is in steady state, gain and loss of the molecules is balance~\cite{braell1984glycoprotein}.
\item Molecules are neither created nor destroyed~\cite{he2009differential}.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments~\cite{fries1981transient}.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing~\cite{mcnew2000compartmental}.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle~\cite{mima2008reconstituted}.
\item An active SNARE pair is necessary and sufficient for fusion~\cite{weber1998snarepins}
. 
\end{enumerate}
%
All our assumptions, except assumption 5, are held up by cell biological results.
%
Although vesicles produced in a cell do vary in size~\cite{jena2008intracellular}, they are much smaller than compartments, hence, for the sake of simplicity, we assume a uniform size for intracellular vesicles.
%The assumptions 
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%
%\begin{example}
%	%
%	In figure~\ref{fig:synth-vts}, we present a partial VTS that has 3 compartments and it's complete VTS by our tool. The synthesis is performed on the basis of steady state property and the  k-connectivity of the graph.
%	
%\end{example}
%\input{synth-dia}

### 2019-04-03 papers/journal/prelim.tex
Updated the 1.2

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.
%

\subsection{Solvers}
\noindent In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

>>>>

Quantified Boolean formulas(QBFs) also allow quantifiers over Boolean variables.
%
For example, $\forall x \exists y. (x \lor y)$, for Boolean variables $x$ and $y$.
%
The formula says that for both the values of $x$ there is a value of $y$
such that $x \lor y$ is 1.
%
The problem of finding satisfying assignment for QBFs is even harder problem~\cite{arora2009computational}.\\
%

\subsubsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC, SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{biere2009conflict}.
%1
The QBF solver add support of quantifiers by adding more rules for quantifiers~\cite{buning2009theory}.

### 2019-04-03 papers/journal/synth-dia.tex
Vts dia update
Updated the 1.2

\begin{figure}[t]
%	\centering
	%\begin{minipage}{0.45\linewidth
 \begin{subfigure}[b]{0.49\linewidth}

	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.0cm,
	  thick,main node/.style={rectangle,draw}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {PM { \^{Qa5} 
	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};

	  %le <-> pm
	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7} (pm);
	  %ee -> le
	  \path (ee) edge[bend right, text width=3.0cm] node [below,rotate=65] {\^{R8},Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
	  \path (pm) edge[bend left=30, text width=2.5cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
	\end{tikzpicture}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.0cm,
	  thick,main node/.style={rectangle,draw}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};

	  %le <-> pm
	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=70] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
	  }}
	  %ee -> le
	  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [above] {\^{R3, {\color{blue} { \textbf{\^{Qa2,}, \^{Qa7}, \^{R2}}}}}} (pm);
	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
	 % \end{scope}
	 \end{tikzpicture}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	%\begin{minipage}{0.45\linewidth
 \begin{subfigure}[b]{0.49\linewidth}
%\begin{tikzpicture}[node distance = 30mm]

\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
\begin{scope}[]

\node[main node] (1) {$s_{1}$};
\node[main node] (2) [below left of=1] {$s_{2}$};
\node[main node] (3) [below right of=1] {$s_{3}$};

\path[every node/.style={font=\sffamily\small}]
(3) edge node [left] {} (1)
(1) edge [loop above] node {} ()
(2) edge [loop above] node {} ()
(1) edge node [right] {} (2)
(2) edge node[right] {} (3)
(3) edge[bend left, below] node{} (2);
%(3) edge [bend right] node[right] {} (2)
\end{scope}
%	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
%	  thick,main node/.style={rectangle,draw}]
%	 % 	\begin{scope}[]
%	  \node[main node] (pm) {08};
%	  \node[main node] (ee) [below right of=pm] {346};
%	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {1 2 7 9};
%	
%	  %le <-> pm
%	  \path (le) edge[bend right=55] node [above] {Qb7 Qc7} (pm);
%	  %ee -> le
%	  \path (ee) edge[bend right=32, text width=2.0cm] node [below,rotate=55] {\^{R8},Qa7, Qbc7,R7} (le);
%	
%	  %pm <-> ee
%	  \path (ee) edge[bend left=32] node [below, rotate=-15] {\^{R3}} (pm);
%	  \path (pm) edge[bend left=30, text width=2.0cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
%	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
%	  thick,main node/.style={rectangle,draw}]
%	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
%	  \node[main node,text width=1.5cm] (pm) {\textbf{PM:} {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7 ...}}};
%	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {\textbf{EE:} {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
%	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {\textbf{LE:} {\small \^{Qa8} \^{Qb8} \^{Qc8 ...}}};
%	  
%	  %le <-> pm
%	  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);
%	  
%	  %le <-> ee
%	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {\color{blue} { {\textbf{\^{R8},Qa7}}}} (ee);
%	  }}
%	  %ee -> le
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {\^{R8},Qa7, Qbc7,R7} (le);	  
%	  
%	  %pm <-> ee
%	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {\^{R3, {\color{blue} { \textbf{\^{Qa2}, \^{Qa7}, \^{R2}}}}}} (pm);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
%	 % \end{scope}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
\begin{scope}[]

\node[main node] (1) {$s_{1}$};
\node[main node] (2) [below left of=1] {$s_{2}$};
\node[main node] (3) [below right of=1] {$s_{3}$};

\path[every node/.style={font=\sffamily\small}]
(3) edge node [left] {} (1)
(1) edge [loop above] node {} ()
(2) edge [loop above] node {} ()
(1) edge node [right] {} (2)
(2) edge node[right] {} (3)
(3) edge[bend left, below] node{} (2);
%(3) edge [bend right] node[right] {} (2)
\end{scope}
	 \end{tikzpicture}
	 \caption{Output complete VTS} 
	 \label{fig:synth-vts2}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in the partial VTS.} \label{fig:synth-vts}
\end{figure}
